---
title: "classify_text"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{classify_text}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autotextclassifier)
library(recipes)
```

# Data munging 

Don't forget to make sure that the type of the outcome variable is factor.

```{r eval = FALSE}
sample_data <- autotextclassifier::sample_data

sample_data$category <- as.factor(sample_data$category)
```

# Apply basic recipe 

The following information is provided by the `rec` object.

> Training data contained 232 data points and no missing data.

> Operations:

> Tokenization for text [trained]
Stop word removal for text [trained]
Text filtering for text [trained]
Term frequency-inverse document frequency with text [trained]

```{r eval = FALSE}
rec_obj <- recipe(category ~ text, data = sample_data)

rec <- apply_basic_recipe(rec_obj, text)
```

